### 2016-10-15 paper/evaluation.tex
Added barplot image

To evaluate the cost of test execution, we first compiled the project
and test source files, later, we measured the elapsed time to run the
tests via the build system. We ignored non-related tasks such as
\emph{javadoc} generation.  We grouped the resulting time from test
execution in four different groups: (1) tests that ran in less than
one minute, (2) one to five minutes, (3) five to ten minutes, and (4)
more than ten minutes to execute. Figure \Fix{x} shows the
distribution of subjects per group. It is important to mention that
Figure \Fix{x} represents a lower bound for elapsed time: since the
subjects were tested in a potentially unstable revision, some tests
may fail, interrupting the execution.

\Fix{Histogram to appear}

>>>>

To evaluate the cost of test execution, we first compiled the project
and test source files, later, we measured the elapsed time to run the
tests via the build system. We ignored non-related tasks such as
\emph{javadoc} generation.  We grouped the resulting time from test
execution in four different groups: tests that ran in less than one
minute (group A), one to five minutes (group B), five to ten minutes
(group C), and more than ten minutes to execute (group D).
Figure~\ref{fig:timecost-barplot} shows the distribution of subjects
per group. It is important to mention that
Figure~\ref{fig:timecost-barplot} represents a lower bound for elapsed
time: since the subjects were tested in a potentially unstable
revision, some tests may fail, interrupting the execution.

\begin{figure}[t]
    \centering
    \includegraphics[width=0.5\textwidth]{plots/timecost-barplot/timecost-barplot.pdf}
    \caption{\Fix{...}}
    \label{fig:timecost-barplot}
\end{figure}
